### 2023-07-04 paper/sec-dis-pseudodata.tex
added discussion in Sect 2

%-----------------------------------------------------------------------
\begin{figure}[!ht]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

%-----------------------------------------------------------------------
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
	\caption{Estimate of the systematic uncertainties at FASER$\nu$2 coming from the final-state 
		lepton energy $E_\ell$ for the inclusive and charm productions. The different markers
		represent the charge of the incoming neutrino.
	}
	\label{fig:percentage_error_elepton}
\end{figure}
%-----------------------------------------------------------------------

>>>>

%-----------------------------------------------------------------------
\begin{figure}[!ht]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{\small The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

Fig.~\ref{fig:percentage_error_elepton}
displays the estimated systematic uncertainties for the  measurements
of the double-differential
neutrino scattering cross-section at FASER$\nu$2.
%
We consider the leading sources of systematic errors,
associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
and to the hadronic energy $E_h$.
%
The size of each source of systematic error is plotted as a function
of the average momentum fraction per bin $\la x\ra$
in three different bins of $Q^2$.
%
We indicate separately the results for neutrino and antineutrino projectiles as well as
those associated to inclusive and to charm production measurements.
%
Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
%
The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the nominal baseline scenario,
and in the case of the latter they are the smallest in the large-$x$ region.
%
Similar overview plots have been produced for the other LHC neutrino experiments
considered in this work.

%-----------------------------------------------------------------------
\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
  \caption{\small Estimated systematic uncertainties for the  measurements
    of the double-differential
    neutrino scattering cross-section at FASER$\nu$2.
    %
    We consider the leading sources of systematic errors,
    associated respectively to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
    and to the hadronic energy $E_h$.
    %
    The size of each source of systematic error is plotted as a function
    of the average momentum fraction per bin $\la x\ra$
    in three different bins of $Q^2$.
    %
    We indicate separately the results for neutrino and antineutrino projectiles as well as
    those associated to inclusive and to charm production measurements.
  }
  \label{fig:percentage_uncertainties_overview}
\end{figure}
%-----------------------------------------------------------------------
